### 2017-11-28 paper/sections/1_introduction.tex
Changed paragraph before list of contribs

% What is Mantle
To design more flexible cache management policies, like our solution in
Figure~\ref{fig:cache-management}, we use the data management language and
policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.  While Mantle
was designed for the narrow purpose of file system metadata load balancing,
this paper provides evidence that the approach is more broad.  Specifically,
the collection of abstractions in Mantle provide a general control plane that
improves the performance of metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running storage system, such as a file system or key-value
store.  Rather than implementing a policy directly into the storage system,
which requires domain-specific knowledge to find and change policies in the
storage system, we separate policies from mechanisms in a general way.  By
exposing just the policies developers unfamiliar with the storage system that
their application uses can quickly deploy efficient solutions based on their
application-specific knowledge.  We show that our framework:

>>>>

% What is Mantle
In this paper we are presenting the successful use of the Mantle policy language and engine to manage the dynamically-sized cache. Mantle provides a control plane that
injects policies into a running storage system, such as a file system or key-value store. While Mantle
was originally designed for file system metadata load balancing~\cite{sevilla:sc15-mantle},
we found that it works surprisingly well for specifying cache management policies without requiring users to possess extensive knowledge about the internals of storage systems. We show that our framework:
